Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Final Draft - WiP}}

### 2014-12-06 Paper.tex
Modified GHOST: allow multiple gnerations of uncles.

The validation of uncle headers means nothing more than verifying that each uncle header is both a valid header and satisfies the relation of uncle to the present block. Formally:
\begin{equation}
\bigwedge_{U \in B_\mathbf{U}} V(U) \; \wedge \; P(U) = P(P(B_H)) \; \wedge \; P(B_H) \neq B
\end{equation}

>>>>

The validation of uncle headers means nothing more than verifying that each uncle header is both a valid header and satisfies the relation of $N$th-generation uncle to the present block where $N \leq 6$. Formally:
\begin{equation}
\bigwedge_{U \in B_\mathbf{U}} V(U) \; \wedge \; k(U, P(B_H), 6)
\end{equation}

where $k$ denotes the ``is-kin'' property:
\begin{equation}
k(U, H, n) \equiv \begin{cases} false & \text{if} \quad n = 0 \\ 
s(U, H) &\\
\quad \vee \; u(U, P(H), n - 1) & \text{otherwise}
\end{cases}
\end{equation}

and $s$ denotes the ``is-sibling'' property:
\begin{equation}
s(U, H) \equiv (P(H) = P(U)\; \wedge \; H \neq U)
\end{equation}
